\documentclass{res} 
\usepackage{xspace}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{hyperref}
\hypersetup{pdfborder= {0 0 1.5 [1 1]},colorlinks=true, urlcolor=blue}
\let\orgLaTeX\LaTeX
\renewcommand*{\LaTeX}{\orgLaTeX\xspace}
\usepackage{anysize}
\marginsize{2cm}{3.5cm}{2cm}{1cm}  
\begin{document}
\begin{center}
\begin{Large}
\textbf{SEBASTI\'{A}N AMADOR\\}
\textbf{Curriculum Vitae}\\
\end{Large}
\begin{small}
\href{mailto:jsamador@ucdavis.edu}{jsamador@ucdavis.edu}\\
(Updated June 2023)
\end{small}
\end{center}
\begin{normalsize}

\section{\textbf{Education}}
\begin{itemize}
\item \textbf{Ph.D. in Economics}, University of California, Davis, 2024 (expected).
\item \textbf{M.A. in Economics}, with honors, Pontificia Universidad Javeriana, 2016.
\item \textbf{B.A. in Economics}, Pontificia Universidad Javeriana, 2012.
\end{itemize}

\section{\textbf{Experience}}
\begin{itemize}
\item  \textbf{Ph.D. Intern (Summer 2022)}.  Bank of Finland, Helsinki, Finland.
\item  \textbf{Research Assistant (Summer 2022)}. University of California (under Professors Katherine Eriksson and Gary Richardson).
\item \textbf{Economist (July 2012 - July 2018)}. Macroeconomic Programming and Inflation Department\\ Colombian Central Bank (Banco de la Rep\'{u}blica), Bogot\'{a}, Colombia.
\item \textbf{Research Assistant (July 2011 - June 2012)}. Macroeconomic Programming and Inflation Department. Colombian Central Bank (Banco de la Rep\'{u}blica), Bogot\'{a}, Colombia.
\end{itemize}

\section{\textbf{Fields of Interest:} Macroeconomics, History, Finance, Long-run development.}

\section{\textbf{Job Market Paper}}
\begin{itemize}
\item \textbf{\textit{Vulnerable adoption: the macroeconomic consequences of endogenous technological adoption and coordination failures.}}
\end{itemize}
\section{\textbf{Working papers}}
\begin{itemize}
\item \href{https://ideas.repec.org/p/cda/wpaper/348.html}{\textbf{\textit{Hysteresis, Endogenous Growth,  and Monetary policy}}} - Nominated for the Winter School 2021 Best Paper Award,  Centre for Development Economics and Econometric Society.
\end{itemize}
\section{\textbf{Work in progress}}
\begin{itemize}
\item \textbf{\textit{Monetary policy,  sectoral reallocation and long-run growth}} - Joint with Michaela Elfsbacka-Schm\"{o}ller,  Ph.D. Internship at the Bank of Finland, 2022.
\end{itemize}
\section{\textbf{Publications}}
\begin{itemize}
\item \href{https://onlinelibrary.wiley.com/doi/abs/10.1111/infi.12128}{\textbf{\textit{Determinants of housing bubbles' duration in OECD countries}}}\\ 
\begin{small}
With G\'{o}mez-Gonzalez, J., and Sanin-Restrepo, S.
\\International Finance, Vol. 21(2), 140-157, 2018.
\end{small}
\item \href{http://www.sciencedirect.com/science/article/pii/S0939362517300328}{\textbf{\textit{Finance Neutral Potential Output: An Evaluation on an Emerging Market Monetary Policy Context}}}\\ 
\begin{small}
Economic Systems, Vol. 41(3), 389-407, 2017.
\end{small}
\item \href{http://www.sciencedirect.com/science/article/pii/S0939362516300292}{\textbf{\textit{Mind the Gap: Computing Finance-Neutral Output Gaps in Latin-American Economies}}}\\
\begin{small}
With Tenjo, F., G\'{o}mez-Gonzalez, J., Ojeda, J., and Jaulin, O.\\ Economic Systems, Vol. 40(3), 335-518, 2016.
\end{small}
\item \href{http://www.elsevier.es/es-revista-ensayos-sobre-politica-economica-387-articulo-credit-business-cycles-causal-effects-S0120448315000421?redirectNew=true}{\textbf{\textit{Credit and Business Cycles: An Empirical Analysis in the Frequency Domain}}}\\ 
\begin{small}
With G\'{o}mez-Gonzalez, J., Gait\'{a}n, C., Villamizar, M. and Z\'{a}rate, H.\\ Ensayos sobre Pol\'{i}tica Econ\'{o}mica, Vol. 33(78), 176-189, 2015.
\end{small}
\item \href{http://rd.springer.com/article/10.1007\%2Fs11408-013-0217-6\#page-1}{\textbf{\textit{Loan Growth and Bank Risk: New Evidence}}} \\ 
\begin{small}
With G\'{o}mez-Gonz\'{a}lez, J.E. and Murcia, A. \\Financial Markets and Portfolio Management, Vol. 27(4) , 365-379, 2013.
\end{small}
\item \href{http://www.banrep.gov.co/es/libro-flujos-capitales}{\textbf{\textit{El Mercado Mundial del Caf\'{e} y su Impacto en Colombia}}}\\ 
\begin{small}
With Caicedo, E., Cano, C., Tique, E. and Vallejo, C.\\ Banco de la Rep\'{u}blica, 2013.
\end{small}
\end{itemize}


\section{\textbf{Awards and Honors}}
\begin{itemize}
\item \textbf{Miguel V\'{e}lez Fellowship} UC Davis Graduate Studies and Economics Department, 2023.
\item \textbf{Research and Travel Award} UC Davis Economics Department, 2022 and 2023.
\item \textbf{Departmental Fellowship} UC Davis, 2018-2019.
\item \textbf{Lauchlin Currie Scholarship for Ph.D. Studies} Banco de la Rep\'{u}blica, 2017.
\item \textbf{Performance Excellence Award} Banco de la Rep\'{u}blica, 2017.
\item \textbf{Javeriana Order of Academic Excellence}, Pontificia  Universidad Javeriana, 2016.
\item \textbf{7$^{th}$ Place Economics ECAES Exam} National exam economics programs, ICFES, 2010-II.
\item \textbf{Honor Mention for Best ECAES Exam} Pontificia Universidad Javeriana, 2010-II.
\item \textbf{1$^{st}$ Place, Economics Essay Contest} Pontificia Universidad Javeriana, 2010 \& 2008.
\item \textbf{Outstanding Academic Performance} Pontificia Universidad Javeriana, 2011 \& 2008.
\end{itemize}

\section{Presentations}
\begin{itemize}
\item Macroeconomics Brownbag, UC Davis,  February 2023,  March 2023, April 2021.
\item Economic History Mini-Workshop, UC Davis, April 2023.
\item American Economic Association Poster Session, New Orleans, January 2023.
\item Midwest Macro Meeting, Southern Methodist University, November 2022.
\item LACEA Meeting,  Universidad del Pacifico, November 2022.
\item Latin American Meeting of the Econometric Society,  Universidad del Pacifico, November 2022.
\item Researchers' LaUNCH, Bank of Finland, September 2022.
\item Bank of Finland's Villa Research Workshop, Bank of Finland, August 2022.
\item Winter School, Centre for Development Economics and Econometric Society, December 2021. 
\item Economic History Brownbag, UC Davis, April 2021.
\item Economics Department Seminar, Pontificia Universidad Javeriana, November 2017, June 2016.
\item Economics Seminar, Banco de la Rep\'{u}blica, Bogot\'{a}, July 2016.
\item Economics Seminar, Banco de la Rep\'{u}blica, Medell\'{i}n, June 2016.
\item XX Meeting of CEMLA, Banco Central de la Rep\'{u}blica Dominicana, October 2015.
\end{itemize}

\section{\textbf{Other Profesional Information}}
\begin{itemize}

\item \textbf{Languages:} Spanish (native), English (fluent).
\item \textbf{Referee for:} Revista de Econom\'{i}a Institucional and Ensayos sobre Pol\'{i}tica Econ\'{o}mica.
\item \textbf{Memberships:} Commission on Wage and Labor Policy Negotiation, Ministry of Labor, Colombia (2012-2018). American Economic Association, Econometric Society, Latin American and Caribbean Economic Association, Western Economic Association.
\end{itemize}

\section{References}
\begin{itemize}

\item \textbf{Òscar Jordà}\\
Senior Policy Advisor - Federal Reserve Bank of San Fransisco\\
Professor of Economics - University of California, Davis\\
E-mail: \href{mailto:ojorda@ucdavis.edu}{ojorda@ucdavis.edu}
\item \textbf{Alan M. Taylor}\\
Distinguished Professor of Economics and Finance -UC Davis\\
E-mail: \href{mailto:amtaylor@ucdavis.edu}{amtaylor@ucdavis.edu}
\item \textbf{Sanjay Singh}\\
Assistant Professor of Economics - UC Davis\\
E-mail: \href{mailto:sjrsingh@ucdavis.edu}{sjrsingh@ucdavis.edu}
\item \textbf{Nicolas Caramp}\\
Assistant Professor of Economics - UC Davis\\
E-mail: \href{mailto:ncaramp@ucdavis.edu}{ncaramp@ucdavis.edu}

\end{itemize}
\end{normalsize}

\end{document}
